Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2022-03-08 papers/04 journal final/journal_v16.tex
final docs

%\vspace{-20pt}
\subsection{Modelling the prosumers}
\label{sec:mod_comp}
In this section, we introduce the prosumer model. We consider that power might be generated by non-dispatchable generation units, e.g. solar and wind-based generators, or dispatchable units, e.g. small-scale fuel-based generators.
%
Moreover, we also consider the slow dynamics of storage units. We restrict the model of each component such that Assumption \ref{as:gen} holds, that is, we avoid non-convex formulations and provide a convex approximation instead. Not only this approach is common in the literature, see e.g.   \cite{moret2020,atzeni2013,molzahn2017}, but also practical especially for real-time implementation, which requires fast and reliable computations.

@@

\smallskip
\paragraph*{Dispatchable units}
The objective function of a dispatchable unit, denoted by $f_{i}^{\mathrm{di}}: \mathbb{R}^{H} \to \mathbb{R}$, is typically a convex quadratic function   \cite{atzeni2013,hans2018,sorin2019}, e.g. 
\begin{equation}
f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) = \|p_{i}^{\mathrm{di}}\|_{Q_i^{\mathrm{di}}}^2+ {(c_i^\mathrm{di})}^\top p_{i}^{\mathrm{di}}, \label{eq:f_dg}
\end{equation}
where $Q_i^{\mathrm{di}}\succcurlyeq0$ and $c_i^{\mathrm{di}}$ are constants.
Furthermore, the power generation $p_{i}^{\mathrm{di}}$ is limited by 
\begin{equation}
\begin{aligned}
\underline{p}_{i}^{\mathrm{di}}\1_{H} \leq p_{i}^{\mathrm{di}} &\leq \overline{p}_{i}^{\mathrm{di}}\1_{H}, \quad& &\forall i\in\mathcal{N}^{\mathrm{di}},\\
p_{i}^{\mathrm{di}} &= 0, \quad& &\forall i\notin\mathcal{N}^{\mathrm{di}},
\end{aligned}
\label{eq:p_dg_bound}	
\end{equation}
where $\overline{p}_{i}^{\mathrm{di}} > \underline{p}_{i}^{\mathrm{di}}\ge 0$ denote maximum and minimum total power production of the dispatchable generation unit, and $\mathcal{N}^{\mathrm{di}}\subseteq\mathcal{N}$ the subset of agents that own dispatchable units.

%\smallskip
\paragraph*{Storage units} 
Each prosumer might also minimize the usage of its storage units, for instance, in order to reduce its degradation. The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$ and defined as in \cite{hans2018}:
\begin{equation}
f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
\end{equation}
where $Q_i^{\mathrm{st}}\succcurlyeq0$. {The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}},
%
\begin{equation}
	\begin{aligned}
	%	\left.
	%	\begin{array}{c}
			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\tfrac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\tfrac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %\forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\[.2em]
		\\
			\underline{x}_i &\leq x_{i,h+1} \leq \overline{x}_i,  \qquad \forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\%[.2em]
			{p}_{i}^{\mathrm{ch}} &\in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],  \quad  \forall i \in \mc N^{\mathrm{st}},
	%	\end{array}
	%	\hspace{-5pt} \right\} & \begin{matrix}
	%	\end{matrix} 
	\\
		p_{i}^{\mathrm{ch}} &= 0, \ \ p_{i}^{\mathrm{ds}}= 0,\qquad \qquad \quad \  \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
, {$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas ${\overline p^{\mathrm{ch}}_i} \geq 0$ and ${\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.

>>>>

%\vspace{-20pt}
\subsection{Modelling the prosumers}
\label{sec:mod_comp}
In this section, we introduce the prosumer model. We consider that power might be generated by non-dispatchable generation units, e.g., solar and wind-based generators, or dispatchable units, e.g., small-scale fuel-based generators.
%
Moreover, we also consider the slow dynamics of storage units. We restrict the model of each component such that Assumption \ref{as:gen} holds, that is, we avoid non-convex formulations and provide a convex approximation instead. Not only this approach is common in the literature, see e.g.   \cite{moret2020,atzeni2013,molzahn2017}, but also practical especially for real-time implementation, which requires fast and reliable computations.

@@

\smallskip
\paragraph*{Dispatchable units}
The objective function of a dispatchable unit, denoted by $f_{i}^{\mathrm{di}}: \mathbb{R}^{H} \to \mathbb{R}$, is typically a convex quadratic function   \cite{atzeni2013,hans2018,sorin2019}, e.g., 
\begin{equation}
f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) = \|p_{i}^{\mathrm{di}}\|_{Q_i^{\mathrm{di}}}^2+ {(c_i^\mathrm{di})}^\top p_{i}^{\mathrm{di}}, \label{eq:f_dg}
\end{equation}
where $Q_i^{\mathrm{di}}\succcurlyeq0$ and $c_i^{\mathrm{di}}$ are constants.
Furthermore, the power generation $p_{i}^{\mathrm{di}}$ is limited by 
\begin{equation}
\begin{aligned}
\underline{p}_{i}^{\mathrm{di}}\1_{H} \leq p_{i}^{\mathrm{di}} &\leq \overline{p}_{i}^{\mathrm{di}}\1_{H}, \quad& &\forall i\in\mathcal{N}^{\mathrm{di}},\\
p_{i}^{\mathrm{di}} &= 0, \quad& &\forall i\notin\mathcal{N}^{\mathrm{di}},
\end{aligned}
\label{eq:p_dg_bound}	
\end{equation}
where $\overline{p}_{i}^{\mathrm{di}} > \underline{p}_{i}^{\mathrm{di}}\ge 0$ denote maximum and minimum total power production of the dispatchable generation unit, and $\mathcal{N}^{\mathrm{di}}\subseteq\mathcal{N}$ the subset of agents that own dispatchable units.

%\smallskip
\paragraph*{Storage units} 
Each prosumer might also minimize the usage of its storage units, for instance, in order to reduce its degradation. The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$ and defined as in \cite{hans2018} as follows:
\begin{equation}
f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
\end{equation}
where $Q_i^{\mathrm{st}}\succcurlyeq0$. {The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}},
%
\begin{equation}
	\begin{aligned}
	%	\left.
	%	\begin{array}{c}
			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\tfrac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\tfrac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %\forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\[.2em]
		\\
			\underline{x}_i &\leq x_{i,h+1} \leq \overline{x}_i,  \qquad \forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\%[.2em]
			{p}_{i}^{\mathrm{ch}} &\in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],  \quad  \forall i \in \mc N^{\mathrm{st}},
	%	\end{array}
	%	\hspace{-5pt} \right\} & \begin{matrix}
	%	\end{matrix} 
	\\
		p_{i}^{\mathrm{ch}} &= 0, \ \ p_{i}^{\mathrm{ds}}= 0,\qquad \qquad \quad \  \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
, {$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas ${\overline p^{\mathrm{ch}}_i} \geq 0$ and ${\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.
